---
title: "S1_dataclean_ABCD"
output: html_document
date: "2024-08-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyverse)
library(ggplot2)
library(tableone)
library(psych)
library(RColorBrewer)
infopath <- "D:/xuxiaoyu/open_dataset_information/ABCD/info"
release5path <- "Y:/abcd-data-release-5.0/abcd-data-release-5.1/core"
demopath <- "D:/xuxiaoyu/DMRI_network_development/Normative_model/demography"
filerecord_base <- read.csv(paste0(infopath, "/filerecord_base.csv"))
filerecord_2year <- read.csv(paste0(infopath, "/filerecord_2year.csv"))
filerecord_4year <- read.csv(paste0(infopath, "/filerecord_4year.csv"))
FigureFolderABCD <- 'D:/xuxiaoyu/DMRI_network_development/Normative_model/Figures_nopremature'

```

## Step1 general exclusion by demographic information

We will keep participants from baseline, 2year-follow up, and 4year-follow up.
Exclusion criteria:
1)Participants were not proficient in English;
2)Parents were not proficient in English or Spanish;
3)Participants with traumatic brain injury history (Mild, moderate, and severe);
4)Participants with uncorrected visual or auditory deficits;
5)Participants with intellectual disability;
6)Participants with major medical or neurological conditions;
7)participants who were premature or had low birth weight;
8)Participants with MRI contraindications.


```{r step1_excluddemo}
demo_sublist_criteria <- read.csv(paste0(infopath, "/demo_sublist_criteria.csv"))
demo_sublist_criteria <- demo_sublist_criteria %>%
  filter(eventname %in% c("baseline_year_1_arm_1", "2_year_follow_up_y_arm_1", "4_year_follow_up_y_arm_1"))
demo_sublist <- demo_sublist_criteria %>% 
  filter(if_language_y==F &
         if_language_p==F &
         if_TBI==F &
         if_sensory==F &
         if_intel==F &
         if_medical==F &
         if_contra==F &
         if_age==F &
         if_gender==F &
         if_premature==F)

num_exclude1_base <- nrow(demo_sublist_criteria[demo_sublist_criteria$eventname=="baseline_year_1_arm_1",]) - nrow(demo_sublist[demo_sublist$eventname=="baseline_year_1_arm_1",])
num_exclude1_2year <- nrow(demo_sublist_criteria[demo_sublist_criteria$eventname=="2_year_follow_up_y_arm_1",]) - nrow(demo_sublist[demo_sublist$eventname=="2_year_follow_up_y_arm_1",])
num_exclude1_4year <- nrow(demo_sublist_criteria[demo_sublist_criteria$eventname=="4_year_follow_up_y_arm_1",]) - nrow(demo_sublist[demo_sublist$eventname=="4_year_follow_up_y_arm_1",])
num_exclude1 = num_exclude1_base+num_exclude1_2year+num_exclude1_4year
print(paste("1st, based on demographic criteria, we excluded", num_exclude1, "visits in total,", num_exclude1_base, "from baseline,", num_exclude1_2year, "from 2year,", num_exclude1_4year, "from 4year."))

```
## Step2 MRI & diagnosis
1) participants with complete MRI data from 3 visits.
2) successfully converted to BIDS.
3) passed official QC.
4) diagnosed as TD; or diagnosed as ADHD at any one of visits.

```{r step2_completeMRI}
demo_sublist$eventname2 <- gsub("_(.)", "\\U\\1", demo_sublist$eventname, perl = T)
table(demo_sublist$eventname2)
demo_sublist$scanID <- paste0(gsub("NDAR_", "sub-NDAR", demo_sublist$src_subject_id),"_ses-", demo_sublist$eventname2)
demo_sublist[,names(demo_sublist)[str_detect(names(demo_sublist), "if_")]] <- NULL
# rbind filerecords
filerecord_base$scanID <- paste0(gsub("NDAR_", "sub-NDAR", filerecord_base$src_subject_id),"_ses-", filerecord_base$eventname2)
filerecord_2year$scanID <- paste0(gsub("NDAR_", "sub-NDAR", filerecord_2year$src_subject_id),"_ses-", filerecord_2year$eventname2)
filerecord_4year$scanID <- paste0(gsub("NDAR_", "sub-NDAR", filerecord_4year$src_subject_id),"_ses-", filerecord_4year$eventname2)
ncol4year <- ncol(filerecord_4year)
filerecord_4year <- cbind(filerecord_4year, data.frame(matrix(NA, nrow(filerecord_4year), ncol(filerecord_2year)-ncol(filerecord_4year))))
names(filerecord_4year)[(ncol4year+1):ncol(filerecord_2year)] <- setdiff(names(filerecord_2year), names(filerecord_4year)[1:ncol4year])
filerecord_all <- rbind(filerecord_base, filerecord_2year, filerecord_4year)
filerecord_all[,c("src_subject_id", "eventname2", "eventname")] <- NULL
demo_sublist <- merge(demo_sublist, filerecord_all, by="scanID", all.x = T)

## 1. complete raw data
demo_sublist2 <- demo_sublist %>% filter(dMRI_size>0 & T1WI_size>0 & fmap_size>0)
# Philips dMRI with less than 102 gradients
index_P_incomplete <- which(demo_sublist2$scanner=="Philips" & demo_sublist2$philips_gradientnum<102)
demo_sublist2 <- demo_sublist2[-index_P_incomplete, ]
num_exclude2_base <- nrow(demo_sublist[demo_sublist$eventname2=="baselineYear1Arm1",]) - nrow(demo_sublist2[demo_sublist2$eventname2=="baselineYear1Arm1",])
num_exclude2_2year <- nrow(demo_sublist[demo_sublist$eventname2=="2YearFollowUpYArm1",]) - nrow(demo_sublist2[demo_sublist2$eventname2=="2YearFollowUpYArm1",])
num_exclude2_4year <- nrow(demo_sublist[demo_sublist$eventname2=="4YearFollowUpYArm1",]) - nrow(demo_sublist2[demo_sublist2$eventname2=="4YearFollowUpYArm1",])

print(paste("2nd,", nrow(demo_sublist2), "have complete MRI data via fasttrack,", num_exclude2_base, "participants were excluded from baseline,", num_exclude2_2year, "participants were excluded from 2year-follow-up,", num_exclude2_4year, "participants were excluded from 4year-follow-up."))

## 2. successful unzip & dcm2nii
demo_sublist3 <- demo_sublist2 %>% filter(if_bids==T)
num_exclude3_base <- nrow(demo_sublist2[demo_sublist2$eventname2=="baselineYear1Arm1",]) - nrow(demo_sublist3[demo_sublist3$eventname2=="baselineYear1Arm1",])
num_exclude3_2year <- nrow(demo_sublist2[demo_sublist2$eventname2=="2YearFollowUpYArm1",]) - nrow(demo_sublist3[demo_sublist3$eventname2=="2YearFollowUpYArm1",])
num_exclude3_4year <- nrow(demo_sublist2[demo_sublist2$eventname2=="4YearFollowUpYArm1",]) - nrow(demo_sublist3[demo_sublist3$eventname2=="4YearFollowUpYArm1",])

print(paste("3rd,", nrow(demo_sublist3), "have been successfully converted to BIDS,", num_exclude3_base, "participants from baseline,", num_exclude3_2year, "participants from 2year-follow-up,", num_exclude3_4year,"participants from 4year-follow-up", "failed unzip or dcm2niix."))

## 3. passed official QC
mri_y_qc_incl <- read.csv(paste0(release5path, "/imaging/mri_y_qc_incl.csv"))
demo_sublist4 <- merge(demo_sublist3, mri_y_qc_incl, by=c("src_subject_id", "eventname"), all.x=T)
demo_sublist4 <- demo_sublist4 %>% filter(imgincl_t1w_include==1 & imgincl_dmri_include==1)

num_exclude4_base <- nrow(demo_sublist3[demo_sublist3$eventname2=="baselineYear1Arm1",]) - nrow(demo_sublist4[demo_sublist4$eventname2=="baselineYear1Arm1",])
num_exclude4_2year <- nrow(demo_sublist3[demo_sublist3$eventname2=="2YearFollowUpYArm1",]) - nrow(demo_sublist4[demo_sublist4$eventname2=="2YearFollowUpYArm1",])
num_exclude4_4year <- nrow(demo_sublist3[demo_sublist3$eventname2=="4YearFollowUpYArm1",]) - nrow(demo_sublist4[demo_sublist4$eventname2=="4YearFollowUpYArm1",])

print(paste("4th,", nrow(demo_sublist4), "passed official QC,", num_exclude4_base, "participants from baseline,", num_exclude4_2year, "participants from 2year-follow-up,",num_exclude4_4year, "participants from 4year-follow-up were excluded due to low imaging quality."))

## 4. Diagnosed as TD or ADHD
demo_sublist_CBCLtrajectory <- read.csv(paste0(demopath, "/demo_sublist_CBCLtrajectory.csv"))
demo_sublist_CBCLtrajectory_ADHDcluster <- read.csv(paste0(demopath, "/demo_sublist_CBCLrawtrajectory_ADHDcluster.csv"))
demo_sublist4 <- demo_sublist4 %>% left_join(select(demo_sublist_CBCLtrajectory, scanID, if_TD, if_ADHD, ADHD_condition, diff_value,ADHD_trajectory, ksads_14_853_p, ksads2_14_809_p, ksads_14_855_p, ksads2_14_811_p, ksads2_14_813_p, ksads_14_856_p, brought_medications, brought_medications_1yr_p, MPH, Amphetamine, alpha_agonist, atomoxetine, SSRI, Other_antidepressants_anxiety, Antipsychotic, adhd_medication, antipsychotic_medication, antidepressant_medication, if_anyADHD_l), by="scanID")

demo_sublist5 <- demo_sublist4 %>% filter(if_TD==1 | if_anyADHD_l==1)
demo_sublist5 <- demo_sublist5 %>% left_join(select(demo_sublist_CBCLtrajectory_ADHDcluster, scanID, class, prob1, prob2), by="scanID")
demo_sublist5$class <- as.factor(demo_sublist5$class)
summary(demo_sublist5[,c("class", "prob1", "prob2")])

num_exclude5_base <- nrow(demo_sublist4[demo_sublist4$eventname2=="baselineYear1Arm1",]) - nrow(demo_sublist5[demo_sublist5$eventname2=="baselineYear1Arm1",])
num_exclude5_2year <- nrow(demo_sublist4[demo_sublist4$eventname2=="2YearFollowUpYArm1",]) - nrow(demo_sublist5[demo_sublist5$eventname2=="2YearFollowUpYArm1",])
num_exclude5_4year <- nrow(demo_sublist4[demo_sublist4$eventname2=="4YearFollowUpYArm1",]) - nrow(demo_sublist5[demo_sublist5$eventname2=="4YearFollowUpYArm1",])

print(paste("5th,", nrow(demo_sublist5), "were diagnozed as TD or ADHD for at least two visits,", num_exclude5_base, "participants from baseline,", num_exclude5_2year, "participants from 2year-follow-up,", num_exclude5_4year, "participants from 4year-follow-up were excluded."))


# 5. finish preprocessing
demo_sublist_unfinished <- demo_sublist5 %>% filter(qsiprep_finished==0 | schaefer400_7_num != 452)
demo_sublist_finished <- demo_sublist5 %>% filter(qsiprep_finished==T)
demo_sublist5_list <- demo_sublist5[,c("src_subject_id", "eventname2", "siteID", "scanner")]
write.csv(demo_sublist5_list, paste0(infopath, "/demo_sublist5_list.csv"), row.names = F)
write.csv(demo_sublist5, paste0(infopath, "/demo_sublist5.csv"), row.names = F)

num_exclude6_base <- nrow(demo_sublist5[demo_sublist5$eventname2=="baselineYear1Arm1",]) - nrow(demo_sublist_finished[demo_sublist_finished$eventname2=="baselineYear1Arm1",])
num_exclude6_2year <- nrow(demo_sublist5[demo_sublist5$eventname2=="2YearFollowUpYArm1",]) - nrow(demo_sublist_finished[demo_sublist_finished$eventname2=="2YearFollowUpYArm1",])
num_exclude6_4year <- nrow(demo_sublist5[demo_sublist5$eventname2=="4YearFollowUpYArm1",]) - nrow(demo_sublist_finished[demo_sublist_finished$eventname2=="4YearFollowUpYArm1",])

print(paste("6th,", nrow(demo_sublist_finished), "SCs were successfully reconstructed,", num_exclude6_base, "participants from baseline,", num_exclude6_2year, "participants from 2year-follow-up,", num_exclude6_4year, "participants from 4year-follow-up were excluded."))

# 6. head motion
demo_sublist6 <- demo_sublist_finished %>% filter(((meanFD<mean(meanFD,na.rm = T)+3*sd(meanFD,na.rm = T)) & (meanFD>mean(meanFD,na.rm = T)-3*sd(meanFD,na.rm = T))) | is.na(meanFD))

num_exclude7_base <- nrow(demo_sublist_finished[demo_sublist_finished$eventname2=="baselineYear1Arm1",]) - nrow(demo_sublist6[demo_sublist6$eventname2=="baselineYear1Arm1",])
num_exclude7_2year <- nrow(demo_sublist_finished[demo_sublist_finished$eventname2=="2YearFollowUpYArm1",]) - nrow(demo_sublist6[demo_sublist6$eventname2=="2YearFollowUpYArm1",])
num_exclude7_4year <- nrow(demo_sublist_finished[demo_sublist_finished$eventname2=="4YearFollowUpYArm1",]) - nrow(demo_sublist6[demo_sublist6$eventname2=="4YearFollowUpYArm1",])

print(paste("7th,", nrow(demo_sublist6), "have acceptable head motion,", num_exclude7_base, "participants from baseline,", num_exclude7_2year, "participants from 2year-follow-up,",num_exclude7_4year, "participants from 4year-follow-up were excluded due to exaggerated head motion."))


```


## Step3 merge demographic information


```{r merge_demo}
demo_sublist6 <- demo_sublist6 %>% select(!(contains("size") | contains("num") | contains("include") | contains("nii")))
demo_sublist6$siteID_r <- demo_sublist6$scanner_manufacturer_pd <- NULL

# age & sex
abcd_p_demo <- read.csv(paste0(release5path,'/abcd-general/abcd_p_demo.csv'))
demo_sublist6$age <- demo_sublist6$interview_age / 12
demo_sublist6 <- demo_sublist6 %>% left_join(select(abcd_p_demo, c("src_subject_id", "demo_sex_v2")), by="src_subject_id", multiple="first")

# handedness
nc_y_ehis <- read.csv(paste0(release5path, '/neurocognition/nc_y_ehis.csv'))
demo_sublist6 <- demo_sublist6 %>% left_join(select(nc_y_ehis, c("src_subject_id", "ehi_y_ss_scoreb")), join_by("src_subject_id"), multiple="first")


# cognition
nc_y_nihtb <- read.csv(paste0(release5path, '/neurocognition/nc_y_nihtb.csv'))
interest_cogvar <- c("src_subject_id", "eventname","nihtbx_flanker_uncorrected", "nihtbx_list_uncorrected", "nihtbx_cardsort_uncorrected", "nihtbx_pattern_uncorrected", "nihtbx_fluidcomp_uncorrected", "nihtbx_cryst_uncorrected", "nihtbx_totalcomp_uncorrected")
demo_sublist6 <- demo_sublist6 %>% left_join(select(nc_y_nihtb, all_of(interest_cogvar)), by=join_by(src_subject_id, eventname))

# merge pfactor
pFactor <- read.csv(paste0(infopath,"/p.factor/BifactorP_baseTo4Year.csv"))
pFactor$eventname2 <- gsub("_", "", pFactor$eventname)
pFactor$eventname <- NULL
demo_sublist7 <- merge(demo_sublist6, pFactor, by.x=c("src_subject_id", "eventname2"), by.y=c("srcsubjectid", "eventname2"), all.x=T)


# CBCL
mh_p_cbcl <- read.csv(paste0(release5path, "/mental-health/mh_p_cbcl.csv"))
mh_p_cbcl <- mh_p_cbcl %>% select(c("src_subject_id", "eventname", ends_with("_r"), ends_with("_t")))
demo_sublist7 <- merge(demo_sublist7, mh_p_cbcl, by=c("src_subject_id", "eventname"), all.x=T)


# SES
abcd_p_demo <- read.csv(paste0(release5path,'/abcd-general/abcd_p_demo.csv'))
demo_sublist7 <- demo_sublist7 %>% left_join(select(abcd_p_demo, c("src_subject_id", "eventname", "demo_comb_income_v2", "demo_roster_v2", "demo_comb_income_v2_l", "demo_roster_v2_l")), join_by("src_subject_id", "eventname"))
demo_sublist7 <- demo_sublist7 %>%
  group_by(src_subject_id) %>%
  mutate(demo_comb_income_v2 = coalesce(demo_comb_income_v2, demo_comb_income_v2_l)) %>%
  mutate(demo_roster_v2 = coalesce(demo_roster_v2, demo_roster_v2_l)) %>%
  ungroup()
demo_sublist7$demo_comb_income_v2_l <- demo_sublist7$demo_roster_v2_l <- NULL
demo_sublist7$totalincome <- dplyr::recode(demo_sublist7$demo_comb_income_v2, 
                                      `1` = 2500, `2` = 8500, `3` = 13999.5, `4` = 20499.5, `5` = 29999.5, `6` = 42499.5, `7` = 62499.5, `8` = 87499.5, `9` = 149999.5, `10` = 200000)
demo_sublist7$interviewYear<-substr(demo_sublist7$interview_date,start=nchar(demo_sublist7$interview_date)-3, stop=nchar(demo_sublist7$interview_date))
demo_sublist7$interviewYear=as.numeric(demo_sublist7$interviewYear)
reference_data <- data.frame(familysize = rep(c(1:12),7),
                             povertyline = c(11880,16020,20160,24300,28440,32580,36730,40890,seq(from=45050, to=(45050+4160*3), by=4160), 12140,16460,20780,25100,29420,33740,38060,42380, 46700,51020,	55340,	59660, 12060,16240,20420,24600,28780,32960,37140,41320, 45500,	49680,	53860,	58040,12490,	16910,	21330,	25750,	30170,	34590,	39010,	43430,	47850,	52270,	56690,	61110,seq(from=12760, to=(12760+4480*11), by=4480), seq(from=12880, to=(12880+4540*11), by=4540), seq(from=12880, to=(13590+4720*11), by=4720)),Year = c(rep(2016,12),rep(2018,12), rep(2017,12), rep(2019,12),rep(2020,12),rep(2021,12),rep(2022,12)))
demo_sublist7 <- merge(demo_sublist7, reference_data,
                          by.x = c("interviewYear", "demo_roster_v2"),
                          by.y = c("Year", "familysize"), 
                          all.x = TRUE)
demo_sublist7$income.adj<-demo_sublist7$totalincome / demo_sublist7$povertyline
summary(demo_sublist7$income.adj)

# race
abcd_p_demo <- read.csv(paste0(release5path,'/abcd-general/abcd_p_demo.csv'))
abcd_p_demo <- abcd_p_demo %>%
  mutate(race_ethnicity = if_else(eventname == "baseline_year_1_arm_1" & is.na(race_ethnicity), 0, race_ethnicity))
abcd_p_demo <- abcd_p_demo %>% group_by(src_subject_id) %>% 
  mutate(race_ethnicity = zoo::na.locf(race_ethnicity)) %>%
  mutate(race_ethnicity = zoo::na.locf(race_ethnicity, fromLast = TRUE, na.rm = F))
abcd_p_demo$race_ethnicity <- as.factor(abcd_p_demo$race_ethnicity)

# 1 = White; 2 = Black; 3 = Hispanic; 4 = Asian; 5 = Other; 0=NA
demo_sublist7 <- demo_sublist7 %>% left_join(select(abcd_p_demo, c("src_subject_id", "eventname", "race_ethnicity")), join_by("src_subject_id", "eventname"))
demo_sublist7$race_ethnicity <- factor(demo_sublist7$race_ethnicity, levels=c(0:5), labels=c("NA","White", "Black", "Hispanic", "Asian", "Other"))
summary(demo_sublist7$race_ethnicity)

# write out
write.csv(demo_sublist7, paste0(demopath, "/demo_sublist7_nopremature.csv"), row.names = F)

```

## 2. age distribution plots and demographic tables.

```{r plots}
fillcolor = brewer.pal(3, "Paired")
demo_sublist7$eventname2 <- as.factor(demo_sublist7$eventname2)
demo_sublist7 <- demo_sublist7 %>% mutate(
  diagnosis_label=case_when(
    class==1 ~ "ADHD-persistent",
    class==2 ~ "ADHD-remitting",
    .default = "TD"
  )
)
demo_sublist7$diagnosis_label <- factor(demo_sublist7$diagnosis_label, levels = c("TD", "ADHD-remitting", "ADHD-persistent"))
demo_sublist7$if_ADHD <- factor(demo_sublist7$if_ADHD, levels=c(TRUE, FALSE), labels=c("ADHD", "TD"))

ggplot(data = demo_sublist7, aes(age, y = ..count.., fill = eventname2)) +
  geom_histogram(binwidth = 0.5, color = "black", position = "stack",linewidth=0.5) +
  facet_wrap(~diagnosis_label, ncol = 1, nrow = 3, scales = "free") +
  labs(x = "Age (years)", y = NULL) +
  #scale_x_continuous(limits = c(9, 16), breaks = c(9,10,11,12,13,14,15,16)) +
  #scale_y_continuous(limits = c(0, 50), breaks = c(0,10, 20,30,40, 50)) +
  scale_fill_manual(values = rep(fillcolor,2))+
  #geom_hline(aes(yintercept = 10), colour = "red", linetype="dashed")+
  theme_classic()+
  theme(panel.background = element_rect(fill="transparent"),
        plot.background = element_rect(fill = "transparent",colour = NA),aspect.ratio = 0.2,
        plot.title = element_text(color = "black", size = 14, hjust = 0.5),
        strip.text = element_text(size = 14, color = "black"),
        strip.background = element_rect(fill = "transparent",colour = NA),
        axis.title = element_text(color = "black", size = 14),axis.line = element_line(linewidth = 0.4),
        axis.ticks = element_line(linewidth = 0.4),
        axis.text = element_text(color = "black", size = 14), 
        legend.text = element_text(color = "black", size = 12),
        legend.title = element_text(color = "black", size = 12))

ggsave(paste(FigureFolderABCD, '/Fig1_Age_distribution_count_ABCD_ADHDtraj.tiff', sep = ''),  width = 20, height = 20, units = "cm")
ggsave(paste(FigureFolderABCD, '/Fig1_Age_distribution_count_ABCD_ADHDtraj.svg', sep = ''), width = 20, height = 20, units = "cm")

length(which(table(demo_sublist7$subID)==3)) # 2336 participants have 2 visits, 279 participants have 3 visits.

length(which(table(demo_sublist7$subID[demo_sublist7$if_anyADHD_l==1])==2)) # 879 ADHD_l have 2 visits, 129 ADHD_l have 3 visits.
length(which(table(demo_sublist7$subID[demo_sublist7$if_TD==1 & demo_sublist7$if_anyADHD_l==0])==3)) # 1457 TD have 2 visits, 154 ADHD_l have 3 visits.

## Description for demographic information
ABCD_vars <- c("age", "demo_sex_v2","eventname", "ehi_y_ss_scoreb", "race_ethnicity", "meanFD", "nihtbx_fluidcomp_uncorrected","GENERAL", "siteID","income.adj","adhd_medication", names(mh_p_cbcl)[3:42])
ABCD_tableone <- CreateTableOne(ABCD_vars,strata=c("diagnosis_label", "eventname"), data = demo_sublist7, factorVars=c("demo_sex_v2", "ehi_y_ss_scoreb", "race_ethnicity", "siteID", "adhd_medication"), test=F)
ABCD_tableone <- as.data.frame(print(ABCD_tableone))
write.csv(ABCD_tableone, paste0(FigureFolderABCD, '/MRIdemographic_info_ADHDtraj.csv'))


## Plot the age distribution for ADHD and TD
################
demo_sublist7.ADHDTD <- demo_sublist7 %>% filter(if_TD==1 | if_ADHD=="ADHD")
ggplot(data = demo_sublist7.ADHDTD, aes(age, y = ..count.., fill = eventname2)) +
  geom_histogram(binwidth = 0.5, color = "black", position = "stack",linewidth=0.5) +
  facet_wrap(~if_ADHD, ncol = 1, nrow = 2, scales = "free") +
  labs(x = "Age (years)", y = NULL) +
  #scale_x_continuous(limits = c(9, 16), breaks = c(9,10,11,12,13,14,15,16)) +
  #scale_y_continuous(limits = c(0, 50), breaks = c(0,10, 20,30,40, 50)) +
  scale_fill_manual(values = rep(fillcolor,2))+
  #geom_hline(aes(yintercept = 10), colour = "red", linetype="dashed")+
  theme_classic()+
  theme(panel.background = element_rect(fill="transparent"),
        plot.background = element_rect(fill = "transparent",colour = NA),aspect.ratio = 0.2,
        plot.title = element_text(color = "black", size = 14, hjust = 0.5),
        strip.text = element_text(size = 14, color = "black"),
        strip.background = element_rect(fill = "transparent",colour = NA),
        axis.title = element_text(color = "black", size = 14),axis.line = element_line(linewidth = 0.4),
        axis.ticks = element_line(linewidth = 0.4),
        axis.text = element_text(color = "black", size = 14), 
        legend.text = element_text(color = "black", size = 12),
        legend.title = element_text(color = "black", size = 12))

ggsave(paste(FigureFolderABCD, '/Fig1_Age_distribution_count_ABCD_ADHDall.tiff', sep = ''),  width = 20, height = 20, units = "cm")
ggsave(paste(FigureFolderABCD, '/Fig1_Age_distribution_count_ABCD_ADHDall.svg', sep = ''), width = 20, height = 20, units = "cm")

length(which(table(demo_sublist7.ADHDTD$subID)==2)) # 1733 participants have 2 visits, 181 participants have 3 visits.

length(which(table(demo_sublist7.ADHDTD$subID[demo_sublist7.ADHDTD$if_ADHD=="ADHD"])==3)) # 161 ADHD have 2 visits, 19 ADHD_l have 3 visits.
length(which(table(demo_sublist7.ADHDTD$subID[demo_sublist7.ADHDTD$if_TD==1])==2)) # 1494 TD have 2 visits, 155 TD have 3 visits.

## Description for demographic information
ABCD_vars <- c("age", "demo_sex_v2","eventname", "ehi_y_ss_scoreb", "race_ethnicity", "meanFD", "nihtbx_fluidcomp_uncorrected","GENERAL", "siteID","income.adj","adhd_medication", names(mh_p_cbcl)[3:42])
ABCD_tableone <- CreateTableOne(ABCD_vars,strata=c("if_ADHD", "eventname"), data = demo_sublist7.ADHDTD, factorVars=c("demo_sex_v2", "ehi_y_ss_scoreb", "race_ethnicity", "siteID", "adhd_medication"), test=F)
ABCD_tableone <- as.data.frame(print(ABCD_tableone))
write.csv(ABCD_tableone, paste0(FigureFolderABCD, '/MRIdemographic_info_ADHDvsTD.csv'))



```




