---
title: "S4_compareSCdeviation_ADHDall_VS_TD"
author:
  - name: Xiaoyu Xu
    orcid: 0000-0002-7349-3366
    email: xuxiaoyu@cibr.ac.cn
    url: https://scholar.google.com/citations?user=G0jeI1AAAAAJl
    affiliation: 
      - name: Chinese Institute for Brain Research, Beijing (CIBR)
        group: CUIZAIXU Lab
        url: https://cuilab.cibr.ac.cn/
date: "2025-07-17"
format: 
  html:
    code-fold: true
    code-tools: true
    theme: Materia
    toc: true
    toc_depth: 3
    toc-expand: 1
    toc_float: true
    toc-location: left
    number-sections: true
    number-depth: 3
    embed-resources: true
---

```{r}
#| label: load-packages-data
#| include: false
rm(list=ls())
library(ggplot2)
library(corrplot)
library(RColorBrewer)
library(tidyverse)
library(mgcv)
library(openxlsx)
library(parallel)
library(scales)
library(psych)
library(reshape)
library(patchwork)
library(MatchIt)
library(tableone)

# set resolution
Yeoresolution <- 17
if (Yeoresolution == 7){
  Yeoresolution.delLM = 6
}else if (Yeoresolution == 17){
  Yeoresolution.delLM = 15
}
element_num <- Yeoresolution.delLM*(Yeoresolution.delLM+1)/2

# input directory
wd <- getwd()
homepath <- str_split_i(wd, "Normative_model", 1)
demopath <- paste0(homepath, '/Normative_model/demography')
interfileFolder <- paste0(homepath, '/Normative_model/interfileFolder_EFNYnoCCNP')
interfileFolder_ABCD <- paste0(homepath, '/Normative_model/interfileFolder_ABCD')
functionFolder <- paste0(homepath, "/Normative_model/functions")
resultFolder <- paste0(homepath, "/Normative_model/results_EFNYnoCCNP")
resultFolder_ABCD <- paste0(homepath, "/Normative_model/results_ABCD")
functionFolder.SCDev <- paste0(homepath, "/SC_development/Rcode_SCdevelopment/gamfunction")
FigureFolder <- paste0(homepath, '/Normative_model/Figures_EFNYnoCCNP/Yeo', Yeoresolution,'/CV75')

source(paste0(functionFolder, "/plotmatrix.R"))
source(paste0(functionFolder, "/index2network.R"))
source(paste0(functionFolder.SCDev, "/SCrankcorr.R"))
source(paste0(functionFolder, "/gam_varyingfactor.R"))
source(paste0(functionFolder.SCDev, "/gam_factor_interaction_disease.R"))
# load data
SCdata.sum75.merge.ADHDTD <- readRDS(paste0(interfileFolder, '/SCdata_Yeo',Yeoresolution, '_CV75_deviations_all.rds'))
SCdata.sum75.merge.ADHDTD$sex <- as.factor(SCdata.sum75.merge.ADHDTD$sex)
SCdata.sum75.merge.ADHDTD$diagnosis <- factor(SCdata.sum75.merge.ADHDTD$diagnosis, levels = c("TD", "ADHD"))

table(SCdata.sum75.merge.ADHDTD$diagnosis, SCdata.sum75.merge.ADHDTD$site)

ABCDresult_child <- readRDS(paste0(interfileFolder_ABCD, "/GroupcompareDeviation_TD-ADHDall_SC_Yeo", element_num, "_child_controlAgeSex.rds"))


```

## Step1 Describe SC difference between ADHD and TD change with age.

1.  Interaction model will be fitted, and then the diagnosis effects will computed at different age.
2.  Posterior distribution of the differences and the corresponding p values will be computed.
3.  FDR correction will be applied and the differences bar plots will be drawn.

```{r}
#| label: step1

dataname <- "SCdata.sum75.merge.ADHDTD"
smooth_var <- "age"
int_var <- "diagnosis"
covariates <- "sex+FD"
knots <- 3
increments <- draws <- 1000

# Deivation-Z scores were compared for each connection.
if (! file.exists(paste0(interfileFolder, "/SCDeviationZ_TD_ADHDall_byage_CV75SC_Yeo", element_num,"_controlsex_all10fold.rds"))){
  set.seed(925)
  diffresultsum <- list()
  n = 0
  for (x in 1:element_num){
    n = n +1
    SClabel<-paste0("SC.", x, "_deviationZ")
    region<-SClabel
    diffresult<-gam.varyingcoefficients(region, zscale = F, dataname, smooth_var, int_var, covariates, knots, set_fx = T, increments, draws, return_posterior_coefficients = T)
    diffresult.metric <- diffresult %>% group_by(age) %>%
      summarise(diff.median = median(slope), se = sd(slope), up975 = quantile(slope, 0.975), lw975 = quantile(slope, 0.025), pvalue = 2*(1- pnorm(abs(mean(slope) / sd(slope)))), Tvalue=(mean(slope) / sd(slope)), SCstrength.TDmedian = median(TD), SCstrength.ADHDmedian = median(`ADHD`))
    diffresult.metric$parcel <- SClabel
    
    diffresultsum[[n]] <- diffresult.metric
  }
  
  saveRDS(diffresultsum, paste0(interfileFolder, "/SCDeviationZ_TD_ADHDall_byage_CV75SC_Yeo", element_num,"_controlsex_all10fold.rds"))
}else{
  diffresultsum <- readRDS(paste0(interfileFolder, "/SCDeviationZ_TD_ADHDall_byage_CV75SC_Yeo", element_num,"_controlsex_all10fold.rds"))
}

# FDR correction
diffresultsum.df <- do.call(rbind, diffresultsum)
diffresultsum.df$Tvalue <- diffresultsum.df$Tvalue*-1
diffresultsum.df <- diffresultsum.df %>% group_by(age) %>%
  mutate(fdr_pvalue = p.adjust(pvalue, method="fdr")) %>% ungroup()
summary(diffresultsum.df$fdr_pvalue)

diffresultsum.df$significance_pvalue_fdr <- (diffresultsum.df$fdr_pvalue < 0.05)
diffresultsum.df$sigT <- diffresultsum.df$Tvalue
diffresultsum.df$sigT[which(diffresultsum.df$pvalue > 0.05)] <- NA
diffresultsum.df$sigT_fdr <- diffresultsum.df$Tvalue
diffresultsum.df$sigT_fdr[which(diffresultsum.df$significance_pvalue_fdr==F)] <- NA

Yeo_10 <- SCrankcorr(data.frame(rand=rnorm(element_num, 0, 1)), "rand", Yeoresolution.delLM, T)
Yeo_10$SCranknotie <- rank(Yeo_10$SCrank, ties.method = "first")
Yeo_10$SClabel <- paste0("SC.", 1:element_num, "_deviationZ")
diffresultsum.df <- diffresultsum.df %>% left_join(Yeo_10, join_by(parcel==SClabel))
diffresultsum.df <- diffresultsum.df %>% arrange(SCranknotie) %>%
  mutate(SCrank_label = factor(paste0("label", SCranknotie), levels=paste0("label", sort(Yeo_10$SCranknotie, decreasing = T))))
summary(diffresultsum.df)
lmthr <- max(abs(diffresultsum.df$Tvalue), na.rm=T)
diffresultsum.df.line <- diffresultsum.df %>% group_by(parcel) %>% filter(significance_pvalue_fdr==T) %>%
  summarise(SCrank_label=unique(SCrank_label),
            minsigage = min(age), maxsigage = max(age))

# filter the edges which the significant age period no more than 0.5
diffresultsum.df.line$agegap <- diffresultsum.df.line$maxsigage - diffresultsum.df.line$minsigage
diffresultsum.df.line <- diffresultsum.df.line %>% filter(agegap >= 0.5)


diffresultsum.df.line2 <- diffresultsum.df %>% group_by(parcel) %>%
  summarise(SCrank_label=unique(SCrank_label),
            flipage = age[which.min(abs(Tvalue))])
rankvector <- as.numeric(gsub("label","", diffresultsum.df.line$SCrank_label))
rankvector2 <- as.numeric(gsub("label","", diffresultsum.df.line2$SCrank_label))

linerange_frame<-data.frame(y=c((rankvector-1), rankvector), xmin=rep(diffresultsum.df.line$minsigage, 2), xmax=rep(diffresultsum.df.line$maxsigage, 2))
linerange_frame2 <- data.frame(x=c(diffresultsum.df.line$minsigage, diffresultsum.df.line$maxsigage), ymin =rep((rankvector-1), 2), ymax =rep(rankvector, 2))
linerange_frame3 <- data.frame(x=c(diffresultsum.df.line2$flipage, diffresultsum.df.line2$flipage), ymin =rep((rankvector2-1), 2), ymax =rep(rankvector2, 2))

ggplot(data=diffresultsum.df)+
  geom_bar(aes(x=age, y=c(rep(1,element_num*1000)), fill = Tvalue, group=SCrank_label,
               color=Tvalue), alpha=0.5, stat = "identity", position = "stack")+
  scale_fill_distiller(type="seq", palette = "RdBu", limits=c(-lmthr, lmthr), direction = -1,na.value ="white") +
  scale_color_distiller(type="seq", palette = "RdBu", limits=c(-lmthr, lmthr), direction = -1,na.value ="white") +
  geom_linerange(data=linerange_frame, aes(y=y, xmin =xmin, xmax =xmax), color="black", linewidth=0.5)+
  geom_linerange(data=linerange_frame2, aes(x=x, ymin =ymin, ymax =ymax), color="black", linewidth=0.5)+
  #scale_x_continuous(breaks = c(8.9, round(median(diffresultsum.df.line2$flipage),1), 15.5))+
  scale_y_continuous(breaks = c(0, 40, 80, 120), expand = expansion(add=c(1,5)))+
  scale_x_continuous(expand = expansion(add=c(0.1,0.1)))+
  #geom_vline(xintercept =round(median(diffresultsum.df.line2$flipage),1), color="red", linetype="dashed")+
  ylab("S-A connectional axis rank")+xlab("Age (years)")+
  labs(color=NULL, fill=NULL)+
  #scale_y_continuous(limits = c(0, element_num))+
  theme_classic()+
  theme(axis.text=element_text(size=18, color='black'),
        axis.title = element_text(size = 18),aspect.ratio = 2.1,
        plot.title=element_text(size=18, color='black', hjust=0.5),
        legend.position = "none")
ggsave(paste0(FigureFolder, '/SCstrength_Age/Deviationcompare/Tvalue_controlsex.tiff'), width=14, height =28, units = "cm")



##############

diffresultsum.df.ABCDEdges <- diffresultsum.df %>% filter(parcel %in% ABCDresult_child$parcel[ABCDresult_child$p.fdr<0.05])
diffresultsum.df.ABCDEdges <- diffresultsum.df.ABCDEdges %>% group_by(age) %>%
  mutate(fdr_pvalue = p.adjust(pvalue, method="fdr")) %>% ungroup()
summary(diffresultsum.df.ABCDEdges$fdr_pvalue)

diffresultsum.df.ABCDEdges$significance_pvalue_fdr <- (diffresultsum.df.ABCDEdges$fdr_pvalue < 0.05)
diffresultsum.df.ABCDEdges$sigT <- diffresultsum.df.ABCDEdges$Tvalue
diffresultsum.df.ABCDEdges$sigT[which(diffresultsum.df.ABCDEdges$pvalue > 0.05)] <- NA
diffresultsum.df.ABCDEdges$sigT_fdr <- diffresultsum.df.ABCDEdges$Tvalue
diffresultsum.df.ABCDEdges$sigT_fdr[which(diffresultsum.df.ABCDEdges$significance_pvalue_fdr==F)] <- NA

rand.df <- data.frame(rand = rnorm(element_num, 0, 1))
Yeo_10 <- SCrankcorr(rand.df, "rand", Yeoresolution.delLM, T)
Yeo_10$SCranknotie <- rank(Yeo_10$SCrank, ties.method = "first")
Yeo_10$SClabel <- paste0("SC.", 1:element_num, "_deviationZ")

diffresultsum.df.ABCDEdges <- diffresultsum.df.ABCDEdges %>% arrange(SCranknotie) %>%
  mutate(SCrank_label = factor(paste0("label", SCranknotie), levels=paste0("label", sort(Yeo_10$SCranknotie, decreasing = T))))
summary(diffresultsum.df.ABCDEdges)
lmthr <- max(abs(diffresultsum.df.ABCDEdges$Tvalue), na.rm=T)
diffresultsum.df.line <- diffresultsum.df.ABCDEdges %>% group_by(parcel) %>% filter(significance_pvalue_fdr==T) %>%
  summarise(SCrank_label=unique(SCrank_label),
            minsigage = min(age), maxsigage = max(age))
diffresultsum.df.line2 <- diffresultsum.df.ABCDEdges %>% group_by(parcel) %>%
  summarise(SCrank_label=unique(SCrank_label),
            flipage = age[which.min(abs(Tvalue))])

rankvector <- as.numeric(gsub("label","", diffresultsum.df.line$SCrank_label))
rankvector2 <- as.numeric(gsub("label","", diffresultsum.df.line2$SCrank_label))
rankvector2 <- rankvector2[order(rankvector2)]

rankvector3 <- rep(0, length(rankvector))
for (i in 1:length(rankvector)){
  rankvector3[i] <- which(rankvector2 == rankvector[i])
}

linerange_frame<-data.frame(y=c((rankvector3-1), rankvector3), xmin=rep(diffresultsum.df.line$minsigage, 2), xmax=rep(diffresultsum.df.line$maxsigage, 2))
linerange_frame2 <- data.frame(x=c(diffresultsum.df.line$minsigage, diffresultsum.df.line$maxsigage), ymin =rep((rankvector3-1), 2), ymax =rep(rankvector3, 2))
linerange_frame3 <- data.frame(x=c(diffresultsum.df.line2$flipage, diffresultsum.df.line2$flipage), ymin =rep((rankvector2-1), 2), ymax =rep(rankvector2, 2))

ggplot(data=diffresultsum.df.ABCDEdges)+
  geom_bar(aes(x=age, y=c(rep(1,6*1000)), fill = Tvalue, group=SCrank_label,
               color=Tvalue), alpha=0.5, stat = "identity", position = "stack")+
  scale_fill_distiller(type="seq", palette = "RdBu", limits=c(-lmthr, lmthr), direction = -1,na.value ="white") +
  scale_color_distiller(type="seq", palette = "RdBu", limits=c(-lmthr, lmthr), direction = -1,na.value ="white") +
  geom_linerange(data=linerange_frame, aes(y=y, xmin =xmin, xmax =xmax), color="black", linewidth=0.5)+
  geom_linerange(data=linerange_frame2, aes(x=x, ymin =ymin, ymax =ymax), color="black", linewidth=0.5)+
  #scale_x_continuous(breaks = c(8.9, round(median(diffresultsum.df.line2$flipage),1), 15.5))+
  scale_y_continuous(breaks = seq(from=0.5, to=5.5, by=1), labels=rankvector2, expand = expansion(add=c(0.5,0.5)))+
  scale_x_continuous(expand = expansion(add=c(0.1,0.1)))+
  #geom_vline(xintercept =round(median(diffresultsum.df.line2$flipage),1), color="red", linetype="dashed")+
  ylab("S-A connectional axis rank")+xlab("Age (years)")+
  labs(color=NULL, fill=NULL)+
  theme_classic()+
  theme(axis.text=element_text(size=18, color='black'),
        axis.title = element_text(size = 18),aspect.ratio = 1,
        plot.title=element_text(size=18, color='black', hjust=0.5))
ggsave(paste0(FigureFolder, '/SCstrength_Age/Deviationcompare/Tvalue_controlsex_10fold_ABCDsig.tiff'), width=14, height =14, units = "cm")

print(paste0("The median max age of significant diagnosis effects was ", median(diffresultsum.df.line$maxsigage),"."))
print(paste0("The median age of diagnosis effects convert is ", median(diffresultsum.df.line2$flipage),"."))

write.csv(diffresultsum.df.line, paste0(resultFolder, "/ADHDTDgroupwise_T_dev_by_age_SC_Yeo", element_num,"_CV75_controlsex_10fold.csv"), row.names = F)

```



## Step2 Describe SC difference between ADHDall VS TD at different visits

1.  Diagnosis effects will be detected at different visits.

```{r}
#| label: step2

SCdata.child <- SCdata.sum75.merge.ADHDTD %>% filter(site=="PKU6") %>% filter(age <=10)
SCdata.adoles <- SCdata.sum75.merge.ADHDTD %>% filter(age >10)
rbind(table(SCdata.child$diagnosis, SCdata.child$sex), table(SCdata.adoles$diagnosis, SCdata.adoles$sex))
#       F   M
# TD   72  83
# ADHD 56 202
# TD   68  77
# ADHD 49 177

## control sex and age
if (str_detect(wd, "cuizaixu_lab")){
  for (dataname in c("SCdata.child", "SCdata.adoles")){
    data.tmp <- get(dataname)
    
    Diagnosis.results <- mclapply(1:element_num, function(x){
      region <- paste0("SC.", x, "_deviationZ")
      print(region)
      if (dataname == "SCdata.adoles"){
        modelformula <- as.formula(sprintf("%1$s ~ diagnosis+s(age, k=3, fx=T)+ sex+FD", region))
        gam.model <- gam(modelformula, REML=TRUE, data = data.tmp)
        modelformula.null <- as.formula(sprintf("%1$s ~ s(age, k=3, fx=T)+ sex+FD", region))
        gam.model.null <- gam(modelformula.null, REML=TRUE, data = data.tmp)
        
        anova.result <- anovaPB(gam.model.null, gam.model, n.sim = 10000, ncpus=1)
        anova.cov.pvalue<-anova.result[2, 5]
        
        lm.model <- gam.model
        mod.result <- summary(gam.model)
        group_diff <- mod.result$p.table[2,1]
        tvalue <- mod.result$p.table[2,3]
      }else{
        covariates <- "sex+FD"
        modelformula <- as.formula(sprintf("%s ~ %s + %s",region, "diagnosis", covariates))
        modelformula.null<-as.formula(sprintf("%s ~ %s",region, covariates))
        lm.model <- lm(modelformula, data = data.tmp)
        lm.model.null <- lm(modelformula.null, data = data.tmp)
        anova.result <- anovaPB(lm.model.null, lm.model, n.sim = 10000, ncpus=1)
        anova.cov.pvalue<-anova.result$`Pr(>F)`[2]
        mod.result <- summary(lm.model)
        tvalue=mod.result$coefficients[2,3]
        group_diff <- mod.result$coefficients[2,1]
      }
      
      
      resid_sd <- sigma(lm.model)
      cohen_d <- group_diff / resid_sd
      
      result.df <- data.frame(parcel=region, group="diagnosis", dataname=dataname, tvalue=tvalue,
                              pvalue=anova.cov.pvalue, cohen_d=cohen_d)
      return(result.df)
    }, mc.cores = 50)
    
    Diagnosis.results.df <- do.call(rbind, Diagnosis.results)
    Diagnosis.results.df$p.fdr <- p.adjust(Diagnosis.results.df$pvalue, method="fdr")
    print(paste(sum(Diagnosis.results.df$p.fdr < 0.05), "edges are significantly different between groups."))
    saveRDS(Diagnosis.results.df, paste0(interfileFolder, "/GroupcompareDeviation_TD-ADHDall_SC_Yeo", element_num, "_", str_split_i(dataname, "SCdata.", 2), "_controlAgeSex.rds"))
    
  }
}

results.df.child <- readRDS(paste0(interfileFolder, "/GroupcompareDeviation_TD-ADHDall_SC_Yeo", element_num, "_child_controlAgeSex.rds"))
results.df.adoles <- readRDS(paste0(interfileFolder, "/GroupcompareDeviation_TD-ADHDall_SC_Yeo", element_num, "_adoles_controlAgeSex.rds"))

results.df.child.ABCDROI <- results.df.child %>% filter(parcel %in% ABCDresult_child$parcel[ABCDresult_child$p.fdr<0.05])

for (i in 1:nrow(results.df.child.ABCDROI)){
  parcel <- results.df.child.ABCDROI$parcel[i]
  parcel <- gsub("SC.", "", parcel)
  parcel <- gsub("_deviationZ", "", parcel)
  
  networklabel <- index2network(as.numeric(parcel))
  results.df.child.ABCDROI$label[i] <- paste0(networklabel[1], "-", networklabel[2])

}


## report results
print(paste0(sum(results.df.child$p.fdr < 0.05), " edges have significant diagnosis effects on SC deviation after FDR correction, for child ", sum(results.df.child$pvalue < 0.05), " edges significant before FDR."))
print(paste0(sum(results.df.adoles$p.fdr < 0.05), " edges have significant diagnosis effects on SC deviation after FDR correction, for adoles. ", sum(results.df.adoles$pvalue < 0.05), " edges significant before FDR."))


SArankresult.child <- SCrankcorr(results.df.child, "cohen_d", Yeoresolution.delLM)
SArankresult.child$agerange <- "child"
SArankresult.adoles <- SCrankcorr(results.df.adoles, "cohen_d", Yeoresolution.delLM)
SArankresult.adoles$agerange <- "adoles"
print(rbind(SArankresult.child, SArankresult.adoles))

#   ds.resolution Interest.var r.spearman p.spearman agerange
# 1            15      cohen_d  0.2167210 0.01742859    child
# 2            15      cohen_d  0.1117948 0.22411929   adoles


## plot effect size
results.df.child$agerange <- "child"
results.df.adoles$agerange <- "adoles"

results.df.all <- rbind(results.df.child, results.df.adoles)
Yeo_10 <- SCrankcorr(data.frame(rand=rnorm(element_num, 0, 1)), "rand", Yeoresolution.delLM, T)
Yeo_10$SClabel <- paste0("SC.", 1:element_num, "_deviationZ")
results.df.all <- results.df.all %>% left_join(Yeo_10, join_by(parcel==SClabel))

lmthr <- max(abs(results.df.all$cohen_d))+0.00001 # 0.198
axeslabels=c("VS.P", "SM.A", "VS.C", "SM.B", "DA.A", "DA.B", "FP.C", "DM.C", "VA.A", "TP", "FP.A", "VA.B", "DM.A", "FP.B", "DM.B") 
axeslabelsGap=T
PaletteSet <- list(Name="RdBu", drirection=-1, lmmin = -lmthr, lmmax = lmthr, anglex=45, angley=45,hjustx = 1, hjusty = 1, vjustx = 1, vjusty=0.5)
for (dataname in c("results.df.child", "results.df.adoles")){
  FigT <- plotmatrix(dataname, "cohen_d", Yeoresolution.delLM, Pvar="p.fdr",NAcol="white", lmthr=lmthr, axeslabels, axeslabelsGap=T, linerange_frame=NA, PaletteSet=PaletteSet, Pvar.noFDR=NA)
  print(FigT)
  ggsave(paste0(FigureFolder, "/SCstrength_Age/Deviationcompare/Matrix12_SCcompare_TD_ADHDall_CohenD_", str_split_i(dataname, "df.", 2),"_controlAgeSex.tiff"), height=18, width=20, units = "cm")
}
# scatter plots

results.df.all$agerange <- factor(results.df.all$agerange, levels=rev(c("child", "adoles")))
ggplot(data=results.df.all)+
  #geom_point(aes(x=SCrank, y=cohen_d, color=agerange), size=2, alpha=1)+
  geom_smooth(aes(x=SCrank, y=cohen_d, color=agerange, fill=agerange), alpha=0.5, method = "lm", linewidth=1.2)+
  scale_fill_manual(values = rev(c("#BDBDBD", "#D9D9D9", "#D1E5F0")))+
  scale_color_manual(values = rev(c("#252525", "#525252", "#2166AC")))+
  scale_x_continuous(breaks = c(0, 40, 80, 120))+
  labs(x="S-A connectional axis rank", y="Diagnosis effect (Cohen's d)")+
  theme_classic()+
  theme(axis.text=element_text(size=23, color="black"), 
          axis.title =element_text(size=23, color="black"),aspect.ratio = 1,
          axis.line = element_line(linewidth = 0.6),
          axis.ticks = element_line(linewidth = 0.6),
          plot.background=element_rect(fill="transparent"),
          panel.background=element_rect(fill="transparent"),
          plot.title = element_text(size=15, hjust = 0.5), legend.position = "none")

ggsave(paste0(FigureFolder, "/SCstrength_Age/Deviationcompare/SAaxis_SCcompare_TD_ADHDall_cohend_all_controlAgeSex.tiff"), height=15, width=15, units = "cm")
ggsave(paste0(FigureFolder, "/SCstrength_Age/Deviationcompare/SAaxis_SCcompare_TD_ADHDall_cohend_all_controlAgeSex.svg"), height=13, width=12, units = "cm")



```



## Step3 Compare SC deviation between ADHDall VS TD using the whole sample

```{r}

if (str_detect(wd, "cuizaixu_lab")){
  set.seed(925)
  knots = 3
  int_var <- "diagnosis"
  Int.results <- mclapply(1:element_num, function(i){
    dependentvar <- paste0("SC.", i, "_deviationZ")
    region <- dependentvar
    dataname <- "SCdata.sum75.merge.ADHDTD"
    smooth_var <- "age"
    covariates <- "sex+FD"
    print(paste("Dependent var is", region, ", independent var is", smooth_var, ", interaction var is", int_var))
    gam.res <- gam.smooth.predict.interaction(region, dataname, smooth_var, int_var, covariates, knots=3, set_fx = T, stats_only=FALSE, increments=100)
    gam.res <- as.data.frame(gam.res)
    gam.res$SClabel <- dependentvar
    
    return(gam.res)
  }, mc.cores=50)
  
  Int.results.df <- do.call(rbind, Int.results)
  saveRDS(Int.results.df, paste0(interfileFolder, "/Deviation_TDtest-ADHDall_SC", element_num,".rds"))
}else{
  Int.results.df <- readRDS(paste0(interfileFolder, "/Deviation_TDtest-ADHDall_SC", element_num,".rds"))
}

Int.results.df_final <- Int.results.df[seq(from=2, to=2*element_num, by = 2),]
Int.results.df_final$anova.int.pvalue.fdr <- p.adjust(Int.results.df_final$anova.int.pvalue, method = "fdr")
Int.results.df_final$anova.disease.pvalue.fdr <- p.adjust(Int.results.df_final$anova.disease.pvalue, method = "fdr")
Int.results.df_final[,3:10] <- lapply(Int.results.df_final[,3:10], as.numeric)
summary(Int.results.df_final)

print(paste0(sum(Int.results.df_final$anova.int.pvalue.fdr < 0.05), " edges have significant interaction age effects by ADHD diagnosis after FDR correction."))
# Yeo17: 2
print(paste0(sum(Int.results.df_final$anova.int.pvalue < 0.05), " edges have significant interaction age effects by ADHD diagnosis before FDR correction."))
# Yeo17: 19
print(paste0(sum(Int.results.df_final$anova.disease.pvalue.fdr < 0.05), " edges have significant diagnosis effects on SC strength after FDR correction."))
# Yeo17: 31
print(paste0(sum(Int.results.df_final$anova.disease.pvalue < 0.05), " edges have significant diagnosis effects on SC strength before FDR correction."))
# Yeo17: 45

tabInt <- Int.results.df_final[Int.results.df_final$anova.disease.pvalue.fdr<0.05,]
print(tabInt)

# plot
## SC deviation group compare
lmthr <- max(abs(Int.results.df_final$T.disease))
axeslabels=c("VS.P", "SM.A", "VS.C", "SM.B", "DA.A", "DA.B", "FP.C", "DM.C", "VA.A", "TP", "FP.A", "VA.B", "DM.A", "FP.B", "DM.B") 
axeslabelsGap=T
PaletteSet <- list(Name="RdBu", drirection=-1, lmmin = -lmthr, lmmax = lmthr, anglex=45, angley=45,hjustx = 1, hjusty = 1, vjustx = 1, vjusty=0.5)

FigintT <- plotmatrix(dataname="Int.results.df_final", "T.disease", ds.resolution=Yeoresolution.delLM, Pvar="anova.disease.pvalue.fdr", NAcol="white", lmthr=lmthr, axeslabels, axeslabelsGap=T, linerange_frame=NA, Pvar.noFDR=NA)

print(FigintT)

ggsave(paste0(FigureFolder, "/SCstrength_Age/Deviationcompare/Matrix", Yeoresolution.delLM,"_DeviationCompare_TD_ADHDall_T.tiff"),FigintT, height=16, width=18, units = "cm")

## SC deviation trajectories group compare
lmthr <- max(abs(Int.results.df_final$anova.int.chisq))
axeslabels=c("VS.P", "SM.A", "VS.C", "SM.B", "DA.A", "DA.B", "FP.C", "DM.C", "VA.A", "TP", "FP.A", "VA.B", "DM.A", "FP.B", "DM.B") 
axeslabelsGap=T
PaletteSet <- list(Name="RdBu", drirection=-1, lmmin = -lmthr, lmmax = lmthr, anglex=45, angley=45,hjustx = 1, hjusty = 1, vjustx = 1, vjusty=0.5)

Figintchisq <- plotmatrix(dataname="Int.results.df_final", "anova.int.chisq", ds.resolution=Yeoresolution.delLM, Pvar="anova.int.pvalue.fdr", NAcol="white", lmthr=lmthr, axeslabels, axeslabelsGap=T, linerange_frame=NA, Pvar.noFDR=NA)

print(Figintchisq)

ggsave(paste0(FigureFolder, "/SCstrength_Age/Deviationcompare/Matrix", Yeoresolution.delLM,"_TrajectoryCompare_TD_ADHDall_chisq.tiff"),Figintchisq, height=16, width=18, units = "cm")



```






